pirouette: the error BEAST2 makes in inferring a phylogeny

### 2019-01-21 article.tex
@Giappo will love this

The second step selects an inference model, using the alignment.
The user can specify to use the generative model or select a best model
from a set of inference models. When selecting the generative model,
the site and clock model used in the alignment simulation are used
in inference. Because the given phylogeny (on which the alignment is based)
may have followed any tree prior (also: speciation model), the user needs
to specify which tree prior is used in inference. When selecting a best
model, the alignment is used to find the inference model that has the
highest evidence (also: marginal likelihood)

The third step infers a Bayesian posterior from the simulated alignment.
From the
DNA alignment a Bayesian posterior is generated, using a user-specified
inference setup. The given tree is compared with all posterior trees, using
a user-specified error measurement setup.

>>>>

The second step selects an inference model, using the alignment.
The user can specify to use the generative model or select a best model
from a set of inference models. 
When selecting the generative model,
the site and clock model used in the alignment simulation are used
in inference. Because the given phylogeny (on which the alignment is based)
may have followed any tree prior (also: speciation model), the user needs
to specify which tree prior is used in inference. 
When selecting a best
model, the alignment is used to find the inference model that has the
highest evidence (also: marginal likelihood) from a set of inference models.
The evidence of an inference model is estimated using a nested-sampling
approach, as decribed in Maturana et al., 2018. The nested sampling is
performed by \verb;babette;, that call the 'NS' BEAST2 package. 
Using BEAST2 packages (in a scripted way) can only be done under Linux and Mac,
which excludes Windows from this way of selecting an inference model.

The third step infers a Bayesian posterior from the simulated alignment,
using the inference model(s) selected in the previous step. The user
can specify the additional parameters needed for a BEAST2 run, which
are the Markov-Chain Monte Carlo (MCMC) setup, 
an optional Most Recent Common Ancestor (MRCA) prior and an RNG seed.
The MCMC setup determines the number of posterior trees sampled.
An MRCA prior allows the inferred phylogeny to have a dated crown age.

The fourth step measures the inference error, using the phylogenies in the
Bayesian posterior.

From the
DNA alignment a Bayesian posterior is generated, using a user-specified
inference setup. The given tree is compared with all posterior trees, using
a user-specified error measurement setup.
